Notes: New gaugings in 3d from three-form

### 2023-06-13 Draft_3dH3.tex
Update warp factor Zeta Omega.
Modifications by Emanuel.

The Ansätze~\eqref{eq:GSSansatz} describe a \textit{consistent} truncation if the following condition is satisfied:
\begin{equation} \label{eq:GenLeibniz}
	\gL_{\ff{U}_{\fl{M}}} {\cU}_{\fl{N}}{}^M = X_{\fl{M}\fl{N}}{}^{\fl{P}}\, \cU_{\fl{P}}{}^M\,,
\end{equation}
with $\cU_{\fl{M}}{}^M = \rho^{-1} \UI_{\fl{M}}{}^M$, $\ff{U}_{\fl{M}} = (\cU_{\fl{M}},\,\Sigma_{\fl{M}})$ and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ a constant tensor. This condition ensures that the factorised form of the Ansätze~\eqref{eq:GSSansatz} is preserved by the generalized Lie derivative, \textit{e.g.}
\begin{equation} \label{eq:GSSexample}
	\begin{aligned}
		D_{\mu}\M(x,Y) &= U_{M}{}^{\fl{M}}(Y)\,U_{N}{}^{\fl{N}}(Y)\,{\cal D}_{\mu}\M_{\fl{MN}}(x)\,,\\
		{\cal L}_{(A_{\mu},B_{\nu})}A_{\mu}(x,Y) &= \rho(Y)^{-1}\,\UI_{\fl{M}}{}^{M}(Y)\,\llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}(x)\,,
	\end{aligned}
\end{equation}
where
\begin{equation} \label{eq:3dCovDeriv}
	{\cal D}_{\mu}\M_{\fl{MN}} = \partial_{\mu}\M_{\fl{MN}}-2\,\A_{\mu}{}^{\fl{P}}X_{\fl{P}(\fl{M}}{}^{\fl{Q}}\M_{\fl{N})\fl{Q}}\,, \quad {\rm and} \quad \llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}=X_{\fl{PQ}}{}^{\fl{M}}\A_{\mu}{}^{\fl{P}}\A_{\nu}^{\fl{Q}} \,.
\end{equation}

Thus, for a given twist matrix $U_{M}{}^{\fl{M}}$ satisfying the consistency condition~\eqref{eq:GenLeibniz}, the action~\eqref{eq:ExFTaction} reduces to three-dimensional ${\cal N}=16$ gauged supergravity \cite{Nicolai:2000sc,Nicolai:2001sv}. The constant tensor $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ plays the role of the embedding tensor of the three-dimensional gauged supergravity, as is clear from its appearance in \eqref{eq:3dCovDeriv} in the gauge-covariant derivative and the gauge algebra of the vector fields. From eq. \eqref{eq:GenLeibniz}, it has the following expression in terms of the twist matrix and $\rho$
\begin{equation}
	\begin{aligned}
		X_{\fl{MN}}{}^{\fl{P}}&=-\rho^{-1}\,\Gamma_{\fl{MN}}{}^{\fl{P}} + \rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}\,f^{\fl{QK}}{}_{\fl{L}}\,\Gamma_{\fl{KM}}{}^{\fl{L}}-\frac{1}{60}\,\rho^{-1}\,f^{\fl{PK}}{}_{\fl{N}}\,f_{\fl{ML}}{}^{\fl{Q}}\,\Gamma_{\fl{KQ}}{}^{\fl{L}}\\
		&\quad-\frac{1}{2}\,\rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}\,f^{\fl{QK}}{}_{\fl{M}}\,\Gamma_{\fl{RK}}{}^{\fl{R}}+\left(\delta_{\fl{M}}{}^{\fl{K}}\delta_{\fl{N}}{}^{\fl{P}}-\frac{1}{2}\,f_{\fl{M}}{}^{\fl{LK}}f_{\fl{NL}}{}^{\fl{P}}\right)\,\xi_{\fl{K}}\,.
	\end{aligned}
\end{equation}
Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=\UI_{\fl{M}}{}^{K}\UI_{\fl{N}}{}^{L}\partial_{K}U_{L}{}^{\fl{P}}$ and the trombone gauging
\begin{equation} \label{eq:Trombone}
	\begin{split}
		\xi_{\fl{M}} %&= 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}U_{\fl{M}}{}^{N} \\
		&= 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1} - \rho^{-1}\, \Gamma_{\ov{N}\ov{M}}{}^{\ov{N}} \,.
	\end{split}
\end{equation}
The embedding tensor is most nicely expressed once projected on the adjoint representation
\begin{equation} \label{eq:symembeddingtensor}
	\begin{aligned}
		X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} &= - 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{P}(\fl{M}}{}^{\fl{Q}}\,f_{\fl{N})\fl{Q}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \\
		&= - 14\,\rho^{-1}\,(\mathbb{P}_{3875})_{\fl{MN}}{}^{\fl{PQ}}\,\Gamma_{\fl{PQ}} - \frac{1}{4}\,\rho^{-1}\,\eta_{\fl{MN}}\,\Gamma_{\fl{P}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \,,
	\end{aligned}
\end{equation}
with the projection of the current $\Gamma_{\fl{MN}} = - \tfrac{1}{60}\,\Gamma_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}}$. In the following, we will focus on gaugings with $\xi_{\fl{M}}=0$.

The three-dimensional action follows from inserting the Ansätze~\eqref{eq:GSSansatz} in the ExFT action~\eqref{eq:ExFTaction}. The expressions of the kinetic and Chern-Simons terms result immediately from eq.~\eqref{eq:GSSexample}
\begin{equation}
	\begin{aligned}
		\mathscr{L}_{\rm kin} &= \frac{1}{240}\,D_{\mu}\M_{MN}D^{\mu}\M^{MN} \underset{\rm gSS}{=} \frac{\rho^{2}}{240}\,{\cal D}_{\mu}\M_{\fl{MN}}{\cal D}^{\mu}\M^{\fl{MN}}, \\
		\mathscr{L}_{\rm CS} &\underset{\rm gSS}{=} -\rho^{-1}\,\varepsilon^{\mu\nu\rho}\,X_{\fl{MN}}\,\A_{\mu}{}^{\fl{M}} \left(\partial_{\nu}\A_{\rho}{}^{\fl{N}}-\frac{1}{3}\,\llbracket\A_{\nu},\A_{\rho}\rrbracket^{\fl{N}}\right)\,.
	\end{aligned}
\end{equation}

@@

Since we are focusing on gaugings with vanishing trombone $\xi_{\fl{M}} = 0$, \eqref{eq:reltrX} implies that the two terms in \eqref{eq:ExtraX2Terms} are proportional and we only need to consider one of these terms in the gauged supergravity potential. Thus, the most general Ansatz for the supergravity potential, for gaugings that have an uplift to 10-/11-dimensional supergravity\footnote{If we do not require the three-dimensional gauged supergravity to arise from a consistent truncation, \eqref{eq:reltrX} may be violated and we need to include both terms of \eqref{eq:ExtraX2Terms}. However, here we are not interested in such gaugings.}, is
\begin{equation} \label{eq:Vexpansion}
	\begin{aligned}
		-V &= X_{\fl{MN}}X_{\fl{PQ}}\left(\alpha\,\M^{\fl{MP}}\M^{\fl{NQ}}+\beta\,\M^{\fl{MP}}\eta^{\fl{NQ}}+\delta\,\eta^{\fl{MP}}\eta^{\fl{NQ}}
		%+\gamma\,\eta^{\fl{MN}}\eta^{\fl{PQ}}
		\right) \\
		&\underset{\rm gSS}{=} \rho^{-2}\bigg(14\,\alpha\,\Gamma_{\fl{MN}}\,\Gamma_{\fl{PQ}}\,\M^{\fl{MP}}\M^{\fl{NQ}}+14\,\alpha\,\Gamma_{\fl{MN}}\,\Gamma_{\fl{PQ}}\,\M^{\fl{MQ}}\M^{\fl{NP}}\\
		&\ \quad +2\,\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma^{\fl{K}}{}_{\fl{N}}+\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\,\Gamma_{\fl{N}}{}^{\fl{K}}+\left(-12\,\alpha+2\,\delta
		%-(62)^2\,\gamma
		\right)\,\Gamma_{\fl{MN}}\,\Gamma^{\fl{MN}}\\
		&\ \quad -2\,\beta\,\M^{\fl{MN}}\Gamma_{\fl{MK}}{}^{\fl{L}}\,\Gamma_{\fl{LN}}{}^{\fl{K}}+\beta\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{L}}\,\Gamma_{\fl{LN}}{}^{\fl{K}}+\left(7\,\alpha+\frac{\beta}{2}\right)\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{K}}\,\Gamma_{\fl{LN}}{}^{\fl{L}}\\
		&\ \quad +14\,\alpha\,\M^{\fl{MN}}\M^{\fl{KL}}f_{\fl{QL}}{}^{\fl{P}}\Gamma_{\fl{PN}}{}^{\fl{Q}}\,\Gamma_{\fl{MK}}\bigg)\,.
	\end{aligned}
\end{equation}
Finally, by requiring
\begin{equation}
	\sqrt{|g|} \mathscr{L}_{\rm int} \underset{\rm gSS}{=} - \sqrt{|\mathring{g}|} V \,,
\end{equation}
the parameters in \eqref{eq:Lintexpansion} and \eqref{eq:Vexpansion} are fixed to
\begin{equation}
	\alpha = \frac{1}{28}\,,\quad \beta = \frac{1}{2}\,,\quad a=1\,,\quad \delta=\frac{13}{28} \,. %, \quad \gamma=0.
\end{equation}
%\CE{Freedom for $\delta$ and $\gamma$: $2\delta-(62)^2\gamma=\rho^{2}(1/2+3/7)$.}
%\EM{MG and EM are confused about this -- we need to chat all together}

@@

We are interested in the maximal solutions of the section condition \eqref{eq:SLnSC} which preserve a $\SL{n} \subset \SL{n+1}$ subgroup. Under this decomposition $\SL{n+1} \rightarrow \SL{n}$ with $V^I = \left( V^i,\, V^0 \right)$, where $i = 1, \ldots, n$, we solve the section condition by having physical coordinates $y^{i0}$ on the $n$-dimensional manifold $M$, i.e. $\partial_{ij} = 0$ for all fields with only $\partial_{i0} \neq 0$. Correspondingly, the generalised tangent bundle, whose sections are in the antisymmetric representation of $\SL{n+1}$ and carry weight $\frac{n-3}{n+1}$, decomposes as
\begin{equation} \label{eq:SLnE}
	E = TM \oplus \Lambda^{n-2} T^*M \,,
\end{equation}
Note that for the case of interest to us, $n=3$, \eqref{eq:SLnE} reduces to
\begin{equation}
	E = TM \oplus T^*M \,,
\end{equation}
and its fibres transform in the $\mathbf{6}$ of $\SL{4} \simeq \SO{3,3}$. It is convenient to also introduce the generalised bundle with fibres in the anti-fundamental of $\SL{n+1}$, which is, similarly, given by
\begin{equation}
	N = T^*M \oplus \Lambda^{n} T^*M \,.
\end{equation}
Sections of $N$ are generalised tensors transforming in the anti-fundamental of $\SL{n+1}$ and carrying weight $\frac{2}{n+1}$. For $V, V' \in \Gamma(E)$ and $W \in \Gamma(N)$, the generalised Lie derivative \eqref{eq:SLnGenLie} reduces to
\begin{equation}
	\begin{split}
		\gL_{V} V' &= [v, v'] + L_{v} \omega'_{(n-2)} - \imath_{v'} d\omega_{(n-2)} \,, \\
		\gL_{V} W &= L_v \omega_{(1)} + L_v \omega_{(n)} - \EM{\alpha} \omega_{(1)} \wedge d\omega_{(n-2)} \,,
	\end{split}
\end{equation}
\EM{(I think $\alpha = 1$ but not 100\% sure)}
where we write $V = v + \omega_{(n-2)}$, $V' = v' + \omega'_{(n-2)}$ and $W = \omega_{(1)} + \omega_{(n)}$ as a formal of vectors and $p$-forms, and $L$ denotes the ordinary Lie derivative and $[v,v']$ the ordinary Lie bracket between vector fields $v$ and $v'$.

We can now describe the $S^n$ consistent truncation using the $\SL{n+1}$ ExFT above. Let $Y^I$, $I = 1, \ldots, n+1$ be the embedding coordinates of $S^{n} \subset \mathbb{R}^{n+1}$, such that $Y^I\, Y_I = 1$. On $S^n$, we can define a parallelisation of $N$ using the generalised frame \EM{Check sign of A! Although I'm pretty confident about it.}
\begin{equation}\label{eq:SnFrame}
	\cU^{\fl{I}} = dY^{\fl{I}} + Y^{\fl{I}}\, vol_{S^n} - A \wedge dY^{\fl{I}} \,,
\end{equation}
where $A$ is an $(n-1)$-potential with field strength $dA = (n-1) vol_{S^n}$, and
\begin{equation}
	vol_{S^n} = \frac{1}{n!}\epsilon_{I_1 I_2 \ldots I_{n+1}} Y^{I_1}\, dY^{I_2} \wedge \ldots \wedge dY^{I_{n+1}} \,,
\end{equation}
is the volume form on $S^n$. The frame in \eqref{eq:SnFrame} has the important property that the $n+1$ generalised tensors are nowhere vanishing since $dY^I = 0$ only when $Y^I = 1$. Therefore, \eqref{eq:SnFrame} provides a generalised parallelisation of $S^n$ in the $\SL{n+1}$ ExFT.

In a local basis, \eqref{eq:SnFrame} gives us a $\GL{n+1}$ matrix, $\cU_I{}^{\fl{I}}$, whose determinant allows us to define the scalar density
\begin{equation} \label{eq:rho}
	\rho = \left(\det \cU_I{}^{\fl{I}}\right)^{-1/2} = \left(\det \mathring{g}\right)^{-1/2} \,,
\end{equation}
with $\mathring{g}$ the round metric on $S^n$. Using \eqref{eq:SnFrame} and \eqref{eq:rho} we can define the $\SL{n}$ twist matrix
\begin{equation} \label{eq:SLnFrame}
	U_I{}^{\fl{I}} = \rho^{2/(n+1)}\, \cU_I{}^{\fl{I}} \,,
\end{equation}
and hence a generalised frame for $E$ or a generalised bundle in any other rep of $\SL{n+1}$.

Evaluating \eqref{eq:SLnFrame} and \eqref{eq:rho} on the northern hemisphere $Y^I = \left( y^i,\, \sqrt{1-y^i y_i}\right)$, $i = 1, \ldots, n$ and using the gauge choice for the potential $A$
\begin{equation}
	A_{ij} = \epsilon_{ijk}\, y^k (1 + K(v)) \,,
\end{equation}
with $v = y^i\, y^i$ and $\epsilon_{ijk}$ the volume form on $S^3$, we precisely recover the $\SL{4}$ twist matrix of \cite{Hohm:2014qga}, i.e.
\begin{equation} \label{eq:SLnTwist}
	\UI_{\fl{I}}{}^I = \begin{pmatrix}
		\left(1-v\right)^{-1/4} \left( \delta_i{}^j + y_i\, y^j K(v) \right) & y_i \left(1-v\right)^{1/4} \\
		y^j \left(1-v\right)^{1/4} K(v) & \left(1-v\right)^{3/4}
	\end{pmatrix} \,.
\end{equation}
Moreover, the generalised frame for $E$ precisely coincides with the twist matrix in \cite{Lee:2014mla,Baguet:2015iou}. \EM{Give it explicitly?}

\EM{To do: Should mention Leibniz parallelisability somewhere and the embedding tensor that arises}

>>>>

The Ansätze~\eqref{eq:GSSansatz} describe a \textit{consistent} truncation if the following condition is satisfied:
\begin{equation} \label{eq:GenLeibniz}
	\gL_{\ff{U}_{\fl{M}}} {\cU}_{\fl{N}}{}^M = X_{\fl{M}\fl{N}}{}^{\fl{P}}\, \cU_{\fl{P}}{}^M\,,
\end{equation}
with $\cU_{\fl{M}}{}^M = \rho^{-1} \UI_{\fl{M}}{}^M$, $\ff{U}_{\fl{M}} = (\cU_{\fl{M}},\,\Sigma_{\fl{M}})$ and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ a constant tensor. This condition ensures that the factorised form of the Ansätze~\eqref{eq:GSSansatz} is preserved by the generalized Lie derivative, \textit{e.g.}
\begin{equation} \label{eq:GSSexample}
	\begin{split}
		D_{\mu}\M(x,Y) &= U_{M}{}^{\fl{M}}(Y)\,U_{N}{}^{\fl{N}}(Y)\,{\cal D}_{\mu}\M_{\fl{MN}}(x)\,,\\
		{\cal L}_{(A_{\mu},B_{\nu})}A_{\mu}(x,Y) &= \rho(Y)^{-1}\,\UI_{\fl{M}}{}^{M}(Y)\,\llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}(x)\,,
	\end{split}
\end{equation}
where \EM{Note corrected sign in first equation!}
\begin{equation} \label{eq:3dCovDeriv}
	{\cal D}_{\mu}\M_{\fl{MN}} = \partial_{\mu}\M_{\fl{MN}} + 2\,\A_{\mu}{}^{\fl{P}}X_{\fl{P}(\fl{M}}{}^{\fl{Q}}\M_{\fl{N})\fl{Q}}\,, \quad {\rm and} \quad \llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}=X_{\fl{PQ}}{}^{\fl{M}}\A_{\mu}{}^{\fl{P}}\A_{\nu}^{\fl{Q}} \,.
\end{equation}

Thus, for a given twist matrix $U_{M}{}^{\fl{M}}$ satisfying the consistency condition~\eqref{eq:GenLeibniz}, the action~\eqref{eq:ExFTaction} reduces to three-dimensional ${\cal N}=16$ gauged supergravity \cite{Nicolai:2000sc,Nicolai:2001sv}. The constant tensor $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ plays the role of the embedding tensor of the three-dimensional gauged supergravity, as is clear from its appearance in \eqref{eq:3dCovDeriv} in the gauge-covariant derivative and the gauge algebra of the vector fields. From eq. \eqref{eq:GenLeibniz}, it has the following expression in terms of the twist matrix and $\rho$
\begin{equation}
	\begin{split}
		X_{\fl{MN}}{}^{\fl{P}}&=-\rho^{-1}\,\Gamma_{\fl{MN}}{}^{\fl{P}} + \rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}\,f^{\fl{QK}}{}_{\fl{L}}\,\Gamma_{\fl{KM}}{}^{\fl{L}}-\frac{1}{60}\,\rho^{-1}\,f^{\fl{PK}}{}_{\fl{N}}\,f_{\fl{ML}}{}^{\fl{Q}}\,\Gamma_{\fl{KQ}}{}^{\fl{L}}\\
		&\quad-\frac{1}{2}\,\rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}\,f^{\fl{QK}}{}_{\fl{M}}\,\Gamma_{\fl{RK}}{}^{\fl{R}}+\left(\delta_{\fl{M}}{}^{\fl{K}}\delta_{\fl{N}}{}^{\fl{P}}-\frac{1}{2}\,f_{\fl{M}}{}^{\fl{LK}}f_{\fl{NL}}{}^{\fl{P}}\right)\,\xi_{\fl{K}}\,.
	\end{split}
\end{equation}
Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=\UI_{\fl{M}}{}^{K}\UI_{\fl{N}}{}^{L}\partial_{K}U_{L}{}^{\fl{P}}$ and the trombone gauging
\begin{equation} \label{eq:Trombone}
	\begin{split}
		\xi_{\fl{M}} %&= 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}U_{\fl{M}}{}^{N} \\
		&= 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1} - \rho^{-1}\, \Gamma_{\ov{N}\ov{M}}{}^{\ov{N}} \,.
	\end{split}
\end{equation}
The embedding tensor is most nicely expressed once projected on the adjoint representation
\begin{equation} \label{eq:symembeddingtensor}
	\begin{split}
		X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} &= - 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{P}(\fl{M}}{}^{\fl{Q}}\,f_{\fl{N})\fl{Q}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \\
		&= - 14\,\rho^{-1}\,(\mathbb{P}_{3875})_{\fl{MN}}{}^{\fl{PQ}}\,\Gamma_{\fl{PQ}} - \frac{1}{4}\,\rho^{-1}\,\eta_{\fl{MN}}\,\Gamma_{\fl{P}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \,,
	\end{split}
\end{equation}
with the projection of the current $\Gamma_{\fl{MN}} = - \tfrac{1}{60}\,\Gamma_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}}$. In the following, we will focus on gaugings with $\xi_{\fl{M}}=0$.

The three-dimensional action follows from inserting the Ansätze~\eqref{eq:GSSansatz} in the ExFT action~\eqref{eq:ExFTaction}. The expressions of the kinetic and Chern-Simons terms result immediately from eq.~\eqref{eq:GSSexample}
\begin{equation}
	\begin{split}
		\mathscr{L}_{\rm kin} &= \frac{1}{240}\,D_{\mu}\M_{MN}D^{\mu}\M^{MN} \underset{\rm gSS}{=} \frac{\rho^{2}}{240}\,{\cal D}_{\mu}\M_{\fl{MN}}{\cal D}^{\mu}\M^{\fl{MN}}, \\
		\mathscr{L}_{\rm CS} &\underset{\rm gSS}{=} -\rho^{-1}\,\varepsilon^{\mu\nu\rho}\,X_{\fl{MN}}\,\A_{\mu}{}^{\fl{M}} \left(\partial_{\nu}\A_{\rho}{}^{\fl{N}}-\frac{1}{3}\,\llbracket\A_{\nu},\A_{\rho}\rrbracket^{\fl{N}}\right)\,.
	\end{split}
\end{equation}

@@

Since we are focusing on gaugings with vanishing trombone $\xi_{\fl{M}} = 0$, \eqref{eq:reltrX} implies that the two terms in \eqref{eq:ExtraX2Terms} are proportional and we only need to consider one of these terms in the gauged supergravity potential. Thus, the most general Ansatz for the supergravity potential, for gaugings that have an uplift to 10-/11-dimensional supergravity\footnote{If we do not require the three-dimensional gauged supergravity to arise from a consistent truncation, \eqref{eq:reltrX} may be violated and we need to include both terms of \eqref{eq:ExtraX2Terms}. However, here we are not interested in such gaugings.}, is
\begin{equation} \label{eq:Vexpansion}
	\begin{aligned}
		-V &= X_{\fl{MN}}X_{\fl{PQ}}\left(\alpha\,\M^{\fl{MP}}\M^{\fl{NQ}}+\beta\,\M^{\fl{MP}}\eta^{\fl{NQ}}+\delta\,\eta^{\fl{MP}}\eta^{\fl{NQ}}
		%+\gamma\,\eta^{\fl{MN}}\eta^{\fl{PQ}}
		\right) \\
		&\underset{\rm gSS}{=} \rho^{-2}\bigg(14\,\alpha\,\Gamma_{\fl{MN}}\,\Gamma_{\fl{PQ}}\,\M^{\fl{MP}}\M^{\fl{NQ}}+14\,\alpha\,\Gamma_{\fl{MN}}\,\Gamma_{\fl{PQ}}\,\M^{\fl{MQ}}\M^{\fl{NP}}\\
		&\ \quad +2\,\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\Gamma^{\fl{K}}{}_{\fl{N}}+\beta\,\M^{\fl{MN}}\,\Gamma_{\fl{MK}}\,\Gamma_{\fl{N}}{}^{\fl{K}}+\left(-12\,\alpha+2\,\delta
		%-(62)^2\,\gamma
		\right)\,\Gamma_{\fl{MN}}\,\Gamma^{\fl{MN}}\\
		&\ \quad -2\,\beta\,\M^{\fl{MN}}\Gamma_{\fl{MK}}{}^{\fl{L}}\,\Gamma_{\fl{LN}}{}^{\fl{K}}+\beta\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{L}}\,\Gamma_{\fl{LN}}{}^{\fl{K}}+\left(7\,\alpha+\frac{\beta}{2}\right)\,\M^{\fl{MN}}\Gamma_{\fl{KM}}{}^{\fl{K}}\,\Gamma_{\fl{LN}}{}^{\fl{L}}\\
		&\ \quad +14\,\alpha\,\M^{\fl{MN}}\M^{\fl{KL}}f_{\fl{QL}}{}^{\fl{P}}\Gamma_{\fl{PN}}{}^{\fl{Q}}\,\Gamma_{\fl{MK}}\bigg)\,.
	\end{aligned}
\end{equation}
Finally, by requiring
\begin{equation}
	\sqrt{|g|} \mathscr{L}_{\rm int} \underset{\rm gSS}{=} - \sqrt{|\mathring{g}|} V \,,
\end{equation}
the parameters in \eqref{eq:Lintexpansion} and \eqref{eq:Vexpansion} are fixed to
\begin{equation}
	\alpha = \frac{1}{28}\,,\quad \beta = \frac{1}{2}\,, \quad \delta=\frac{13}{28}\,, \quad a=1 \,. %, \quad \gamma=0.
\end{equation}
%\CE{Freedom for $\delta$ and $\gamma$: $2\delta-(62)^2\gamma=\rho^{2}(1/2+3/7)$.}
%\EM{MG and EM are confused about this -- we need to chat all together}

@@

We are interested in the maximal solutions of the section condition \eqref{eq:SLnSC} which preserve a $\SL{n} \subset \SL{n+1}$ subgroup. Under this decomposition $\SL{n+1} \rightarrow \SL{n}$ with $V^I = \left( V^i,\, V^0 \right)$, where $i = 1, \ldots, n$, we solve the section condition by having physical coordinates $y^{0i}$ on the $n$-dimensional manifold $M$, i.e. $\partial_{ij} = 0$ for all fields with only $\partial_{0i} = \partial_i \neq 0$. Correspondingly, the generalised tangent bundle, whose sections are in the antisymmetric representation of $\SL{n+1}$ and carry weight $\frac{n-3}{n+1}$, decomposes as
\begin{equation} \label{eq:SLnE}
	E = TM \oplus \Lambda^{n-2} T^*M \,,
\end{equation}
Note that for the case of interest to us, $n=3$, \eqref{eq:SLnE} reduces to
\begin{equation}
	E = TM \oplus T^*M \,,
\end{equation}
and its fibres transform in the $\mathbf{6}$ of $\SL{4} \simeq \SO{3,3}$. It is convenient to also introduce the generalised bundle with fibres in the anti-fundamental of $\SL{n+1}$, which is, similarly, given by
\begin{equation}
	N = T^*M \oplus \Lambda^{n} T^*M \,.
\end{equation}
Sections of $N$ are generalised tensors transforming in the anti-fundamental of $\SL{n+1}$ and carrying weight $\frac{2}{n+1}$. For $V, V' \in \Gamma(E)$ and $W \in \Gamma(N)$, the generalised Lie derivative \eqref{eq:SLnGenLie} reduces to
\begin{equation}
	\begin{split}
		\gL_{V} V' &= [v, v'] + L_{v} \omega'_{(n-2)} - \imath_{v'} d\omega_{(n-2)} \,, \\
		\gL_{V} W &= L_v \omega_{(1)} + L_v \omega_{(n)} + \omega_{(1)} \wedge d\omega_{(n-2)} \,,
	\end{split}
\end{equation}
where we write $V = v + \omega_{(n-2)}$, $V' = v' + \omega'_{(n-2)}$ and $W = \omega_{(1)} + \omega_{(n)}$ as a formal of vectors and $p$-forms, and $L$ denotes the ordinary Lie derivative and $[v,v']$ the ordinary Lie bracket between vector fields $v$ and $v'$.

We can now describe the $S^n$ consistent truncation using the $\SL{n+1}$ ExFT above. Let $Y^I$, $I = 1, \ldots, n+1$ be the embedding coordinates of $S^{n} \subset \mathbb{R}^{n+1}$, such that $Y^I\, Y_I = 1$. On $S^n$, we can define a parallelisation of $N$ using the generalised frame
\begin{equation}\label{eq:SnFrame}
	\cU^{\fl{I}} = dY^{\fl{I}} + Y^{\fl{I}}\, vol_{S^n} - dY^{\fl{I}} \wedge A \,,
\end{equation}
where $A$ is an $(n-1)$-potential with field strength $dA = (n-1) vol_{S^n}$, and
\begin{equation}
	vol_{S^n} = \frac{1}{n!}\epsilon_{I_1 I_2 \ldots I_{n+1}} Y^{I_1}\, dY^{I_2} \wedge \ldots \wedge dY^{I_{n+1}} \,,
\end{equation}
is the volume form on $S^n$. The frame in \eqref{eq:SnFrame} has the important property that the $n+1$ generalised tensors are nowhere vanishing since $dY^I = 0$ only when $Y^I = 1$. Therefore, \eqref{eq:SnFrame} provides a generalised parallelisation of $S^n$ in the $\SL{n+1}$ ExFT.

In a local basis, \eqref{eq:SnFrame} gives us a $\GL{n+1}$ matrix, $\cU_I{}^{\fl{I}}$, whose determinant allows us to define the scalar density
\begin{equation} \label{eq:rho}
	\rho = \left(\det \cU_I{}^{\fl{I}}\right)^{-1/2} = \left(\det \mathring{g}\right)^{-1/2} \,,
\end{equation}
with $\mathring{g}$ the round metric on $S^n$. Using \eqref{eq:SnFrame} and \eqref{eq:rho} we can define the $\SL{n}$ twist matrix
\begin{equation} \label{eq:SLnFrame}
	U_I{}^{\fl{I}} = \rho^{2/(n+1)}\, \cU_I{}^{\fl{I}} \,,
\end{equation}
and hence a generalised frame for $E$ or a generalised bundle in any other rep of $\SL{n+1}$. For example, in the generalised tangent bundle \eqref{eq:SLnE}, we have the generalised frame $\cU_{\fl{I}\fl{J}}{}^{IJ} = \left(\det \mathring{g}\right)^{1/2} \cU_{[\fl{I}}{}^{I} \cU_{\fl{J}]}{}^J$, with components given by
\begin{equation} \label{eq:SLnGenFrame}
	2\, \cU_{\fl{I}\fl{J}} = v_{\fl{I}\fl{J}} + \star dY_{\fl{I}\fl{J}} + \imath_{v_{\fl{I}\fl{J}}} A \,,
\end{equation}
where $v_{\fl{I}\fl{J}}$ are the $\SO{n+1}$ Killing vectors of the round $S^n$, matching precisely the $\SL{n+1}$ parallelisations constructed in \cite{Lee:2014mla}.

Using \eqref{eq:SLnGenLie}, we can easily check that the generalised frame  \eqref{eq:SLnGenFrame}, \eqref{eq:SLnTwist} defines a generalised Leibniz parallelisation. In particular, using $dA = (n-1) vol_{S^n}$, we obtain the embedding tensor
\begin{equation}
	\gL_{\cU_{\fl{I}\fl{J}}} \cU^{\fl{K}} = - X_{\fl{I}\fl{J}\fl{L}}{}^{\fl{K}}\, \cU^{\fl{L}} \,,
\end{equation}
with
\begin{equation} \label{eq:SLnEmbeddingTensor}
	X_{\fl{I}\fl{J},\fl{L}}{}^{\fl{K}} = - \delta_{\fl{L}[\fl{I}} \delta_{\fl{J}]}^{\fl{K}} \,.
\end{equation}

Finally, we can also connect the above with the $\SL{n+1}$ Ansatz construction of \cite{Hohm:2014qga}. We do this by evaluating \eqref{eq:SLnFrame} and \eqref{eq:rho} on the northern hemisphere $Y^I = \left( y^i,\, \sqrt{1-y^i y_i}\right)$, $i = 1, \ldots, n$ and using the gauge choice for the potential $A$
\begin{equation}
	A_{i_1 \ldots i_{n-1}} = \epsilon_{i_1 \ldots i_{n-1}j}\, y^j (1 + K(v)) \,,
\end{equation}
with $v = y^i\, y^i$ and $\epsilon_{i_1 \ldots i_{n-1}j}$ the volume form on $S^n$. With the above choices, we precisely recover the $\SL{n+1}$ twist matrix of \cite{Hohm:2014qga}, i.e.
\begin{equation} \label{eq:SLnTwist}
	\UI_{\fl{I}}{}^I = \begin{pmatrix}
		\left(1-v\right)^{-1/(n+1)} \left( \delta_i{}^j + y_i\, y^j K(v) \right) & y_i \left(1-v\right)^{(n-1)/(2(n+1))} \\
		y^j \left(1-v\right)^{(n-1)/(2(n+1))} K(v) & \left(1-v\right)^{\tfrac{n}{n+1}}
	\end{pmatrix} \,.
\end{equation}
